Population Differentiation Analysis

### 2017-07-05 doc/RMD/pop-diff.Rmd
add cross-validation; make dapc black and white

```{r dapc-region, fig.width = 7, fig.height = 7}
region.dapc <- dapc(dat11cc, strata(dat11cc)$Region, n.pca = 25, n.da = 14)
scatter(region.dapc, scree.pca = TRUE,
        bg = "grey80",
        col = funky(nlevels(strata(dat11cc)$Region)), 
        posi.pca = "topright"
        )
ggcompoplot(region.dapc, setPop(dat11cc, ~Region), pal = funky, cols = 2)
```

>>>>

```{r dapc-region-calc, fig.width = 8, fig.height = 7, cache = TRUE}
set.seed(2017-07-05)
region.xval <- xvalDapc(tab(dat11cc), strata(dat11cc)$Region, n.pca = 15:25, 
                        n.rep = 100, parallel = "multicore", ncpus = 4)
region.dapc <- region.xval$DAPC
```

```{r dapc-region, fig.width = 9, fig.height = 8, cache = TRUE}
scatter(region.dapc, 
        scree.pca = TRUE,
        bg = "grey95",
        col = "black",
        # col = rev(funky(nlevels(strata(dat11cc)$Region))), 
        pch = seq(nlevels(strata(dat11cc)$Region)),
        legend = "true",
        posi.leg = "topleft",
        posi.pca = "topright"
        )
ggcompoplot(region.dapc, setPop(dat11cc, ~Region), pal = rev(funky(nlevels(strata(dat11cc)$Region))), cols = 2)
```
